Oregon Sensitivty Analysis

### 2018-09-27 r_scripts/analysis/asthma_pos_sensitivity_results.Rmd
Changed some labels.

```{r append_results, echo=F}
plot_results <- sen_results %>% 
  mutate(scenario = paste0('All Events: ', ref_period)) %>% 
  select(-term, -ref_period) %>% 
  bind_rows(old_results) %>% 
  filter(pos != 'Ambulance') %>% 
  mutate(pos = case_when(pos == 'Emergency Room Hospital' ~ 'Emergency Department', 
                         pos == 'Pharmacy' ~ 'SABA Fill',
                         TRUE ~ pos))

ggplot(data=plot_results, aes(x=scenario, y = estimate, color = scenario, group = scenario)) +
  geom_point() +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), width = 0.2) +
  geom_hline(yintercept = 1, linetype=2) +
  facet_wrap(~pos, scales = 'free_y') +
  ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in PM"[2.5]))) +
  xlab("Outcome") +
  # plot theme
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        # strip element
        strip.background = element_rect(colour=NA, fill=NA),
        panel.border = element_rect(fill = NA, color = "black"),
        # facet text size
        strip.text = element_text(size = 10),
        # axis element (tilt)
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 0.7),
        #axis.title.x = element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_text(angle = 90),
        legend.position = 'bottom')
```

@@

```{r}
other_vis <- unique_vis %>% 
  ungroup() %>% 
  # filter by place of service
  filter(pos_simple %in% c('Ambulance', 'Emergency Room Hospital', 
                           'Inpatient Hospital', 'Office', 'Outpatient Hospital',
                           'Pharmacy', 'Urgent Care')) %>% 
  # find other visit day
  mutate(other_vis_day = lubridate::wday(fromdate, label = T)) %>% 
  select(personkey, pos_simple, other_vis_day) %>% 
  group_by(personkey, pos_simple, other_vis_day) %>% 
  summarize(n = n()) %>% 
  spread(other_vis_day, n)
```

>>>>

```{r append_results, echo=F}
plot_results <- sen_results %>% 
  mutate(scenario = paste0('All Events: ', ref_period)) %>% 
  filter(scenario != 'All Events: Month') %>% 
  select(-term, -ref_period) %>% 
  bind_rows(old_results) %>% 
  filter(pos != 'Ambulance') %>% 
  mutate(pos = case_when(pos == 'Emergency Room Hospital' ~ 'Emergency Department', 
                         pos == 'Pharmacy' ~ 'SABA Fill',
                         TRUE ~ pos)) %>% 
  rename(Scenario = scenario)

ggplot(data=plot_results, aes(x=Scenario, y = estimate, color = Scenario, group = Scenario)) +
  geom_point() +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), width = 0.2) +
  geom_hline(yintercept = 1, linetype=2) +
  facet_wrap(~pos, scales = 'free_y') +
  ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in WFS PM"[2.5]))) +
  xlab("Outcome") +
  # plot theme
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        # strip element
        strip.background = element_rect(colour=NA, fill=NA),
        panel.border = element_rect(fill = NA, color = "black"),
        # facet text size
        strip.text = element_text(size = 10),
        # axis element (tilt)
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 0.7),
        #axis.title.x = element_blank(),
        #axis.ticks.x = element_blank(),
        axis.title.y = element_text(angle = 90),
        legend.position = 'bottom')
```

@@

```{r}
other_vis <- unique_vis %>% 
  ungroup() %>% 
  # filter by place of service
  filter(pos_simple %in% c('Ambulance', 'Emergency Room Hospital', 
                           'Inpatient Hospital', 'Office', 'Outpatient Hospital',
                           'Pharmacy', 'Urgent Care')) %>% 
  # find other visit day
  mutate(other_vis_day = lubridate::wday(fromdate, label = T)) %>% 
  select(personkey, pos_simple, other_vis_day) %>% 
  group_by(personkey, pos_simple, other_vis_day) %>% 
  summarize(n = n()) #%>% 
  #spread(other_vis_day, n)
```

Summary stats per person
```{r}
sum_stats <- other_vis %>% 
  group_by(personkey, pos_simple) %>% 
  summarize(n = n()) %>% 
  group_by(pos_simple) %>% 
  summarize(n_person = n(), n_visit = sum(n))
```

```{r}
persons <- asthma_cohort %>% 
  group_by(personkey) %>% 
  summarize(n = n())
```
